---
title: "Binomial Regression"
output: html_document
date: '2022-03-30'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Binomial Regression Model

For when response variable  is binomially distributed (probabilities of k successes on n trials.)

for binomial response we need 2 sets of info about the response

y:
 successes
n:
  number of trials
  
OR
n-y:
  number of failures


## Example: Challenger Disaster

This is a dataset examining the failure of the O-rings (important component of a space shuttle) under certain conditions 

```{r}
library(tidyverse)
library(faraway)
```


### Linking function in Binomial Regression

The link function is how the predictors are related to the response variable. 

In binomial regression, the three common link functions are *Logit*, *Probit* and *Complimentary Log-Log*

They can be used in the GLM model to define how the response fits the predictor. 


#### Logit link model

```{r}
logitmod<-glm(cbind(damage,6-damage)~temp, family=binomial(), data=orings)
summary(logitmod)
```


#### Probit link model

```{r}
probitmod<-glm(cbind(damage,6-damage)~temp, family=binomial(link=probit),orings)
summary(probitmod)
```



Note how the difference in the link functions changes the dynamics of the fit to the data



```{r}
plot (damage/6 ~ temp, orings, xlim=c(25,85),
ylim=c(0,1),
 xlab="Temperature", ylab="Prob of damage")
x <- seq(25,85,1)
lines(x,ilogit(11.6630−0.2162*x))
lines(x, pnorm(5.5915-0.1058*x), lty=2) 

```


## Inference

Much like Poisson or Logistic regression. Models are compared to a *saturated model* (i.e. a perfect fit to the data) as opposed to a null model. This changes the way we interpret our p-values


```{r}
pchisq(deviance(logitmod), df.residual(logitmod),lower=FALSE)
```
recall:

H_0: our model (less complex)

H_A: saturated model (more complex)

since the P-value is HIGH, we say that it fits the data well



### Confidence Intervals 

Another method of interpreting our model. If the confidence interval includes zero, then you could reject the model and build something else


```{r}
library(MASS)
confint(logitmod)
```



### Odds

