---
title: "Binomial Regression"
output: html_document
date: '2022-03-25'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Conditions for Binomial vs Poisonn 

1.

count is some number out of a possible total. *model this with a binomial* BUT for small success probabilities and LARGE totals, Poisson is a good approximation. 

EX:

modeling incidence of rare forms of cancer. Number of people affected is a small proportion of the population given a geographical area.

if $\mu=np$ while $n\rightarrow\infty$ then B(n,p) is well approximated by $Pois(\mu)$

NOTE:

for a small p, $logit(p)\approx log(p)$

so use of Poisson with a log link is comparable to the binomial with a logit link

2.

Probability of occcurrence of an event in a given time interval is proportional to the length of that time interval and independent of the occurence of other events.

Number of events in any specified time interval will be Poisson distributed

EX:

modeling the number of incoming telephone calls to a service center or the number of earthquakes.

rate of incoming telephone calls is likely to vary with time of day, while the timing of earthquakes are unlikely to be completely independent. However it might be a good approximation



## Poisson Example



The dataset discoveries lists the numbers of great inventions 
and scientific discoveries in each year from 1860 to 1959. Has the 
discovery rate remained constant over time?


```{r}
data(discoveries)



year=1860:1959
g=glm(discoveries ~ year, family="poisson")
summary(g)$coef['year','Pr(>|z|)']
```

