---
title: "simple_lin_categorical_predictor"
author: "Jack Wright"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Categorical Variables

also called **factor** or **qualitative variables**

limited number of values, or levels

```{r}
library(car)
Salaries<-Salaries
```

categorical variable with `n` levels will be transformed into n-1 variables each with 2 levels.

```{r}
levels(Salaries$rank)
```

This 3 level variable will be recoded into 2 variables *AssocProf* and *Prof*

-If rank = AssocProf, then the column AssocProf would be coded with a 1 and Prof with a 0.
-If rank = Prof, then the column AssocProf would be coded with a 0 and Prof would be coded with a 1.
-If rank = AsstProf, then both columns “AssocProf” and “Prof” would be coded with a 0.


recoding this way creates a `contrast matrix`

```{r}
res<-model.matrix(~rank,data=Salaries)
head(res)
```



## Make Model

```{r}
summary(model_anova)
```

## Interpretation

There are 2 dummy variables, where the negative case is `AssistProf`




Estimate is not a slope, but a  difference in group averages (AssistProf vs AssocProf and AssistProf vs Prof)


## Goodness of fit tests

the p-value is valid for this model

the confidence intervals are valid for this model

```{r}
confint(model_anova)
```


```{r}
resid_panel(model_anova)
```

