---
title: "simple linear regression flowchart"
author: "Jack Wright"
date: "11/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


## Requirements for simple linear regression
Response Requirements
1.

`n(response==1)`
2.
`response!=binary & response!=count`
 IF `response==binary`
 use *simple_logistic_regression.Rmd*
 IF `response==count`
 use *simple_count_regression.Rmd*
3.
  IF `response` is an average value at a level of `predictor`, and the standard devaition can be calculated, 
      use *wls_given_variance.Rmd* 

Predictor Requirements

1.
`n(predictor==1)`
  IF 
  `n(predictor!=1)` 
   use *multivariate_regression.Rmd*
2.
`predictor!=factor & predictor!=binary`
  IF 
  `predictor==factor` 
   use *simple_lin_categorical_predictor.Rmd*
  IF
  `predictor==binary`
  use *simple_lin_dummy.Rmd*


`if (response==count)`{
`hist(respone)=approx_normal`
}


## Exploratory Data Analysis

FUNCTIONS:

GGally::ggpairs(data)
-check correlation

corrplot::corrplot(cor(data))

## Patterns to look for

see *common_transformation_patterns.Rmd*


## Build model list

```{r}
model_list<-list()
```


```{r}
x<-seq(1,20)
y<-x^2
y_error<-50*runif(20)*sample(-1:1,20,replace = TRUE)
y<-y+y_error

df_exp<-data.frame(x,y)%>%mutate(y=ifelse(y<0,0,y))
ggplot(df_exp,aes(x=x,y=y))+geom_point()
```


```{r}
model_list[['base']]<-lm(y~x,data=df_exp)
summary(model_list[['base']])


```

## Check for heteroscedasticity

```{r}
library(lmtest)
lmtest::bptest(model_list[['base']])
```
H_0: homoscedasitcity is present (residuals are distributed with equal variance)

H_A: heteroscedasticity is present (residuals are not distributed with equal variance) USE *homoscedasticity_FAIL.Rmd*


if `lmtest::bptest(model)==H_A` perform Weighted least squares


### Examine residuals

```{r}
resid_panel(model_list[['base']])
```



## use powertransform to get the optimal power to raise the response to, and run model again


```{r}
(p1<-powerTransform(df_exp))


model_list[['transform']]<-lm(y^p1$lambda[[2]]~x,data = df_exp)

summary(model_list[['transform']])
resid_panel(model_list[['transform']])
```


## Comparing models

```{r}
#function for looking at adjusted r squared values
lapply(model_list, function(f) list(adj.r.squared=summary(f)$adj.r.squared,beta_estimate=f$coefficient[[2]],confidence_interval=confint(f)))
```

