---
title: "simple_linear_with_dummy_variable"
author: "Jack Wright"
date: "11/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Requirements for simple linear regression with dummy variable

response variable

`is.continuous(dependent_variable)`

predictor variable

`is.binary(predictor_variable)`

```{r message= FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(AER)
```

```{r}
data('CASchools')
df<-CASchools
df<-df%>%dplyr::mutate(STR=as.numeric(students)/as.numeric(teachers))
## Create binary predictor with threshold
df<-df%>%mutate(D=STR<20)%>%mutate(score=(read+math)/2)
```

```{r}
library(car)
car::powerTransform(df%>%select(c(score)))
```

## Estimate Dummy regression Model

```{r}
m.list<-list()
m.list[['lm.dummy']]<-lm(score~D, data=df)
m.list[['lm.d_transform']]<-lm(score^-.207~D, data=df)
```



## Examine Summary

```{r}
summary(m.list[['lm.dummy']])
```

```{r}
lapply(X=m.list,
       FUN = summary)
```

## Suggested Transformations

none


## Interpretation

Estimate is not a slope, but a  difference in group averages (DTRUE vs DFALSE)
## Check Vailidity of Model

```{r}
ggResidpanel::resid_panel(m.list[['lm.dummy']])
```
Since the predictor is binary, we are only looking at the QQ and the Density vs Residuals , and maybe the Cook's distance for leverage. 


## Confidence interval 

```{r}
confint(m.list[['lm.dummy']])
```


Reject null hypothesis since 0 falls outside of the confidence interval