---
title: "linear_weighted_least_squares|variance across predictor"
author: "Jack Wright"
date: "11/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
```

## Requirements for weighted least squares regression

`response`= mean across level of `predictor` 

`sd(response_i|predictor_i)=TRUE`

OR `heteroscedasticity_test(simple_lin_reg)=FAIL`


`response`= mean across level of `predictor` 

`sd(response_i|predictor_i)=TRUE`


## Build model list

```{r}
clean<-read.table(here('data','cleaningwtd.txt'),header=TRUE)
m.list<-list()
m.list[['wls_no_weight']]<-lm(Rooms~Crews,data=clean)
summary(m.list[['wls_no_weight']])
```



## Check for heteroscedasticity

```{r}
library(lmtest)
lmtest::bptest(m.list[['wls_no_weight']])

```

H_0: homoscedasitcity is present (residuals are distributed with equal variance)

H_A: heteroscedasticity is present (residuals are not distributed with equal variance)

if `lmtest::bptest(model)==H_A` perform Weighted least squares

```{r}
m.list[['wls']]<-lm(Rooms~Crews,weights=1/StdDev^2,data=clean)

summary(m.list[['wls']])
```



## Compare fits

```{r}
library(GGally)

ggplot(clean, aes(x=Crews,y=Rooms))+geom_point()+geom_abline(aes(intercept=m.list[['wls']]$coefficients[[1]],slope=m.list[['wls']]$coefficients[[2]],color='wls'))+geom_abline(aes(intercept=m.list[['wls_no_weight']]$coefficients[[1]],slope=m.list[['wls']]$coefficients[[2]],color='unweighted'))
```

